
\courseTemplate[
code = {COMS3000},
title = {Information Security},
score = {4},
prereq = {For COMS3000 prereq: CSSE2310;
For COMS7003 prereq: CSSE7231},
contact = {2L, 1T},
coordinator = {Dr David Ross (dross@itee.uq.edu.au)},
assessment = {
Marked Tutorials & 20\% & Tutorial sheets, handed in electronically and physically. \\
Report & 20\% & A report / essay about a provided topic. \\
Final Exam & 60\% & An open book short response exam. \\
},
review = {
    This course provides a broad but comprehensive overview of the basics of information security. In particular, it covers concepts around access control, information theory, cryptography, network security, cloud security, payment card security and industrial control system security.\\
    
    The lectures are recorded, but attending them is recommended since Dr Ross asks questions of the class and does examples on the whiteboard, which do not appear on recordings. Further, the lectures are worth engaging in since Dr Ross, in addition to teaching at the university, works as an information security professional in industry and as such has a lot of insight into practical aspects of the course.\\
    
    The tutorials in 2016 were mediocre but the marked tutorial sheets must be handed both online at the beginning of the week, and then again at the end of the tutorial (you are able to change your answers during discussion in the tutorial, so the sheets are essentially free marks). The tutorial sheets do provide good study materials and practice questions for the final exam.\\
    
    The report is expected to be quite in depth, with research based on peer-reviewed literature. Students are given a choice of two topics and the report is designed to be an overview of the state of information security in the chosen area.\\
    
    The final exam is open book and in 2016 was reasonably easy, with several questions being repeated or similar to past exams, and all questions being doable with notes and a good understanding of the course material.\\
    
    Overall, this course provides an interesting overview of the InfoSec field, with the added benefit of being taught by someone who actually applies the content for a living. Recommended if you are considering InfoSec as a career path or have a general interest in the field.
},
preparation = {
    \item Complete CSSE2310 and/or COMS3200 to have a background understanding of the TCP/IP / OSI networking stack
    \item Do background reading on information security, best practices and notable threats
}]{}
