
\courseTemplate[
code = {ENGG1100},
title = {Engineering Design},
score = {2},
prereq = {None},
contact = {1W, 1L, 1S, 2P},
coordinator = {A/Professor Lydia Kavanagh (l.kavanagh@uq.edu.au) \& A/Prof Carl Reidsema (c.reidsema@uq.edu.au)},
assessment = {
Handouts & 3\% & Worksheets completed in weekly workshop sessions \\
Plagiarism Module & P\/F & Online interactive questionnaire \\
Preliminary Report & 20\% & Initial research report into group task \\
Project Plan & P\/F & Project Scoping Package \\
Reflections & 3\% & Bi-Weekly Ethical Reflections \\
Peer Assessment & P\/F & Two online peer assessments \\
Attendance & P\/F & Compulsory attendance at several semester events \\
Demo Day & 30\% & Group project demonstration performance \\
Workbook & 14\% & Semester long research log \\
Project Report & 30\% & Group report on project \\
},
review = {
    ENGG1100 is the bane of every engineering student's first semester. The course takes a \'flipped classroom\' approach to teaching, putting most of the burden on the students to make sure things get done. In the copious (and compulsory)  contact hours you'll cover the basics of problem solving as it pertains to engineering. 

    You'll be placed in a group of six for the semester, some of these people will invariably let you down. If you can get past all of that, you may even find yourself enjoying the challenges you face. Throughout the semester you'll work together to complete various stages of what will become a final project (Previous cohorts have built mine sweepers and rescue boats).

    There are many small pieces of assessment throughout the semester but none of them are overly difficult. The hardest part is making sure you don't miss any, as they're all time sensitive. Demo Day performance is largely luck-dependent, but even if your team does poorly on the day you can generally save your marks with the Final Report.

    Most people won't value this course until later in their studies (if ever), but if you want to be an engineer you'll have to brave ENGG100 regardless.    
},
preparation = {
    All you can do is pray.
}]{}
